ActiveCA: Time Use Data from the General Social Survey of Canada to Study Active Travel

### 2025-06-01 paper/Manuscript-Data-Package-1Round-Review.Rmd
Create a document with all manuscript changes and add answer letters for the reviewers.

---
title: "ActiveCA: Time Use Data from the General Social Survey of Canada to Study Active Travel"
author:
  - name: "Anon1"
    email: "Anon1@anon.org"
    affiliation: CODE
    footnote: 1
  - name: "Anon2"
    email: "Anon2@anon.org"
    affiliation: CODE
  - name: "Anon3"
    email: "Anon3@anon.org"
    affiliation: CODE
address:
  - code: CODE
    address: "Some school"
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: 
  "This paper describes {ActiveCA}, an open data product with Canadian time use data. {ActiveCA} is an `R` data package that contains analysis-ready data related to active travel spanning almost 40 years, extracted from cycles 2 (1986), 7 (1992), 12 (1998), 19 (2005), 24 (2010), 29 (2015), and 34 (2022) of the Time Use Survey (TUS) cicles from the General Social Survey (GSS). Active travel is characterized by mode, with walking being part of every cycle and bicycling starting in 1992. The attributes of active trips are the types of locations of origins and destinations, the duration of trips, and episode weights for expanding the trips to population-wide estimates. Based on the year of the survey, a variety of locations are coded. In earlier cycles, these include home, work or school, and other's home, whereas in later cycles these are augmented with locations such as grocery stores, restaurants, outdoor destinations, and others. The geographical resolution includes the province and whether the episode was in an urban or rural setting."

@@

{ActiveCA} is distributed as an `R` package with a number of data 
objects and their documentation. `R` packages contain code, data, and documentation
in a standardized format that can be installed by `R` users via a software repository,
such as CRAN (Comprehensive R Archive Network) or GitHub, which makes them an 
adroit medium to distribute analysis-ready data.

@@

The Public Use Microdata are released by Statistics Canada in two files: a 
_Main file_ and an _Episode file_. The files are linked by keys that identify 
households, individuals, and episodes (i.e., activities) conducted by individuals.
We discuss these files in more detail in the following section.

## The _Main file_

The _Main file_ of the time use survey compiles a large array of aggregated data, 
summarizing the answers to the questionnaire that describe households and 
individuals, as well as derived variables that summarize the respondents' use of 
time use across different activities, locations, and social interactions. This 
file documents the time and duration that respondents allocate to each activity 
and location. The _Main file_ provides a overview of daily routines and social 
dynamics, not focusing on individual activity episodes. Additionally, this file 
categorizes activities into bigger groups and subcategories, facilitating the 
data's analytical utility with additional metrics such as total transit time, time 
spent with household members, and counts of activities and episodes.

Table \ref{tab:main-2015-unprocessed} shows the first ten rows and first six variables of the TUS PUMF 2015 _Main file_ (Cycle 29). Each row in the table correspond to a survey respondent, while the columns refer the following information: record identification (`PUMFID`), the person's weight (`WGHT_PER`), the month the survey data was collected (`SURVMNTH`), the respondent's age group (`AGEGR10`), the respondent's sex (`SEX`), and the respondent's marital status (`MARSTAT`).

The _Main file_ of the 2015 GSS surveys includes a total of 17,390 respondents, representing `r sum(gss_m_2015$WGHT_PER)` individuals and 848 variables.  For discrete variables, Statistics Canada has assigned specific codes to the possible values, with each code accompanied by a label. For instance, in the case of the variable `SURVMNTH`, a value of `1` means `January 2016`, 2 means `February 2016`, 3 corresponds to `March 2016`, and so on.

@@

```{r gss-main-file-2015}
main_2015_unprocessed <- gss_m_2015[1:10, 1:6]  |>
  kable(
    format = "latex", 
    booktabs = TRUE, 
    longtable = TRUE, 
    align = c(rep("c", ncol(gss_m_2015[1:10, 1:6]))),
    caption = "\\label{tab:main-2015-unprocessed}Visualization of the first ten lines and first six columns of the Main file of the 2015 GSS.") |>
  kable_styling(full_width = FALSE, 
                #latex_options=c("striped", "scale_down"), 
                latex_options=c("scale_down"),
                 font_size = 8) |>
  footnote(general = c("Legend: `PUMFID`: record identification. `WGHT_PER`:  person weight. `SURVMNTH`: survey month of data collection. `AGEGR10`: age group of the respondent. `SEX`: sex of the respondent. `MARSTAT`: marital status of the respondent."), threeparttable = T)

@@

## The _Episode file_

The episode is a much bigger file that records detailed data for each activity 
episode reported by respondents. Each episode represents a single activity and its
duration, and the sum of all episodes throughout the day adds up to 24 hours. Each
entry in this file includes the start and end times of the activity, the duration,
location, and accompanying social context, informing when and where activities 
occurred and with whom. The focus of the _Episode file_ is not on the characteristics
of the respondents, but on the characteristics of the activities, and the data 
are structured around the numerous activity instances that compose a day of the 
respondent. Although respondent-specific characteristics are not included within
the _Episode file_, it is possible to link the _Main file_ and the _Episode file_ by 
using a key present in both the _Main_ and _Episode files_.

Similar to Table \ref{tab:main-2015-unprocessed}, which displayed an example of the _Main file_ structure, Table \ref{tab:ep-2015-unprocessed} presents the first seven episodes for the record identification number `10041` and some variables from the TUS PUMF 2015 _Episode file_ (Cycle 29). Each row in the table corresponds to an episode associated with the specified record identification (`PUMFID = 10041`), including the episode's weight (`WGHT_EPI`), episode number (`EPINO`), activity code (`TUI_01`), episode duration (`DURATION`), and episode location (`LOCATION`).

In total, the _Episode file_ of the 2015 GSS surveys contains 274,108 records, representing `r sum(gss_e_2015$WGHT_EPI)` episodes and 527 variables detailing the episodes. Similar to the _Main file_, Statistics Canada has created codes for the discrete variables, with each value corresponding to a label.

In the case illustrated in Table \ref{tab:ep-2015-unprocessed}, this respondent began the diary description by sleeping at home (`TUI_01 = 1` and `LOCATION = 300`) for 210 minutes, followed by 40 minutes of personal hygiene (`TUI_01 = 2`). The respondent then spent 15 minutes on personal care activities, such as getting ready for school, supervising homework, reading, playing, reprimanding, or providing educational or emotional support, as indicated by `TUI_01 = 27`. Next, they recorded a travel episode, walking for 15 minutes (`TUI_01 = 7` and `LOCATION = 315`), where both the origin and destination were their home. Such trips, where the journey starts and finishes at home, can be classified as recreational or leisure trips. Next, the respondent spent 3 hours searching for a job (`TUI_01 = 9`), took a 15-minute lunch break (`TUI_01 = 6`), and then cleaned the house (`TUI_01 = 18`) for two hours. Table \ref{tab:ep-2015-unprocessed} displays only six variables out of the 527 available. As shown, since the dataset does not label the variable values, decoding them can be both time-consuming and challenging.

```{r gss-epi-file-2015}
ep_2015_unprocessed <- gss_e_2015 |>
  filter(PUMFID == 10041 & EPINO <= 7) |>
  dplyr::select(PUMFID, EPINO,WGHT_EPI,TUI_01, DURATION, LOCATION) |>
  kable(
    format = "latex", 
    booktabs = TRUE, 
    longtable = TRUE, 
    align = c(rep("c", ncol(gss_m_2015[1:10, 1:6]))),
    caption = "\\label{tab:ep-2015-unprocessed}Visualization of the seven first episodes of the record number `10041`.") |>
  kable_styling(full_width = FALSE, 
                #latex_options=c("striped", "scale_down"), 
                latex_options=c("scale_down"),
                 font_size = 8) |>
  footnote(general = c("Legend: `PUMFID`: record identification. `EPINO`: episode number. WGHT_EPI: episode's weight. TUI_01: activity code. DURATION: episode's duration. LOCATION: episode's location."), threeparttable = T)

@@

Figure \ref{fig:process-figure} presents a diagram illustrating the processes applied to the _Main_ and _Episode files_ to create the {ActiveCA} datasets. For each TUS cycle, we reviewed the _Episode files_ to identify movement episodes involving walking or cycling. This allowed us to also select the activities immediately before and after the movement episode, helping to infer the trip’s purpose and determine its origin and destination. Active trips were identified by their corresponding activity codes, accounting for variations across survey cycles.

@@

For the _Main files_, we selected socioeconomic variables to help profile individuals engaged in active travel episodes. These included key indicators such as age group, sex, marital status, and number of children, among others. As with the _Episode files_, we labeled and factored the coded variables. Using the appropriate identifiers, we joined the Episode and _Main files_ to determine the province and the type of population centre - whether it is a CMA, a Census Agglomeration (CA), or a non-CMA/CA area.

As output, the {ActiveCA} package provides processed datasets of walking and cycling episodes by year, a unified dataset that contains all walking and cycling episodes across TUS cycles, and processed _Main files_ (not unified, as socioeconomic and demographic variables and their categories differ across TUS cycles).

@@

Table \ref{tab:processed-obs} displays the total number of records processed for Main and _Episode files_. For the _Main files_, a total of `r sum(df_main_processed$Count)` records were processed, referring to all records from the Time Use Surveys from 1986 to 2022, that together represents more of `r sum(df_main_processed$Weighted)` respondents. It also presents the total cases of active trips episodes identified. In total `r sum(df_ep_processed$Count)` records with register of active travel activity. Together, these records account for `r sum(df_ep_processed$Weighted)` episodes.

@@

Table \ref{tab:main-2015-processed} shows the first ten rows and first six variables of the TUS PUMF 2015 Main File (Cycle 29), displayed in \ref{tab:main-2015-unprocessed} before our processing. Table \ref{tab:ep-2015-processed} presents the walking episodes for the record identification number `10041` from the TUS PUMF 2015 _Episode file_ (Cycle 29), previously displayed in Table \ref{tab:ep-2015-unprocessed}. Only the unique active travel episode appear in Table \ref{tab:ep-2015-processed} since the records were filtered to select cases with walking or cycling episodes. For both cases, Tables \ref{tab:main-2015-processed} and \ref{tab:ep-2015-processed} contain labeled variables, facilitating the interpretation of the data.

```{r gss-processed-file-2015, echo=FALSE, cache=FALSE}
main_2015_processed <- gss_main_2015[1:10, 1:6]  |>
  kable(
    format = "latex", 
    booktabs = TRUE, 
    longtable = TRUE, 
    align = c(rep("c", ncol(gss_m_2015[1:10, 1:6]))),
    caption = "\\label{tab:main-2015-processed}Visualization of the first ten lines and first six columns of the 2015 TUS Main File.") |>
  kable_styling(full_width = FALSE, 
                #latex_options=c("striped", "scale_down"), 
                latex_options=c("scale_down"),
                 font_size = 8) |>
  footnote(general = c("Legend: `PUMFID`: record identification. `WGHT_PER`:  person weight. `SURVMNTH`: survey month of data collection. `AGEGR10`: age group of the respondent. `SEX`: sex of the respondent. `MARSTAT`: marital status of the respondent."), threeparttable = T)

@@

ep_2015_unprocessed <- gss_episodes_renamed |>
  filter(PUMFID == 10041 & YEAR == 2015) |>
  dplyr::select(PUMFID, WGHT_EPI, act_label, DURATION, orig_label, dest_label, MODE) |>
  kable(
    format = "latex", 
    booktabs = TRUE, 
    longtable = TRUE, 
    caption = "\\label{tab:ep-2015-processed}Visualization of the active travel episode for the record number `10041` of the 2015 GSS survey.", 
       col.names = c("PUMFID", "WGHT_EPI","Activity","Duration","Origin", "Destination", "Mode")) |> 
  kable_styling(full_width = FALSE, 
                #latex_options=c("striped", "scale_down"), 
                latex_options=c("scale_down"),
                 font_size = 8) |>
  footnote(general = c("Legend: `PUMFID`: record identification. `EPINO`: episode number. WGHT_EPI: episode's weight. TUI_01: activity code. DURATION: episode's duration. LOCATION: episode's location."), threeparttable = T)

@@

# Latex table
median_duration_table <- median_duration_cma |>
  kable(
    format = "latex", 
    booktabs = TRUE, 
    caption = "\\label{tab:cma-durations}Differences in walking duration between provinces and population centre type.") |>
  kable_styling(full_width = FALSE, 
                #latex_options=c("striped", "scale_down"), 
                latex_options=c("scale_down"),
                 font_size = 8) |>
  add_header_above(c(" " = 1, "Population centre type" = 2)) |> 
  footnote(general = c("'CMA' denotes Census Metropolitan Area and 'CA' denotes Census agglomeration."), threeparttable = T)

@@

{ActiveCA} also provides a Jupyter Notebook containing a Python script that demonstrates how to read R data files (.rda) and convert them into Pandas DataFrames. This process allows users to work with and utilize the datasets available in {ActiveCA} within a Python project.

@@

The value of {ActiveCA} lies in its transparency, accessibility, and ease of use,
which facilitates the addition of complementary data sets in the future. `R` users
can seamlessly explore TUS walking and cycling episodes, 
with the option to suggest enhancements to the package as needed. This article adopts
the structure proposed by Anastasia and Páez [-@soukhov2023], whose work provided
essential guidance for the creation of this package. Similarly, we aim to contribute
to the academic community by promoting transparent research practices that encourage
replication and innovation in related fields. We believe that {ActiveCA} will serve
as a basis for further research on TUS and for the integration of additional data by
the authors or the wider open source community.

@@

https://user.fm/files/v2-3d261d0b2aa47fcad096cd9e49fd5cf8/ActiveCA.zip

>>>>

---
title: "ActiveCA: Time Use Data from the General Social Survey of Canada to Study Active Travel"
author:
  - name: "Anon1"
    email: "Anon1@anon.org"
    affiliation: CODE
  - name: "Anon2"
    email: "Anon2@anon.org"
    affiliation: CODE
  - name: "Anon3"
    email: "Anon3@anon.org"
    affiliation: CODE
address:
  - code: CODE
    address: "Some school"
footnote:
  - code: 1
    text: "Corresponding Author"
abstract: 
  "This paper describes {ActiveCA}, an open data product with Canadian time use data. {ActiveCA} is an R data package that contains analysis-ready data related to active travel spanning almost 40 years, extracted from cycles 2 (1986), 7 (1992), 12 (1998), 19 (2005), 24 (2010), 29 (2015), and 34 (2022) of the Time Use Survey (TUS) cicles from the General Social Survey (GSS). Active travel is characterized by mode, with walking being part of every cycle and bicycling starting in 1992. The attributes of active trips are the types of locations of origins and destinations, the duration of trips, and episode weights for expanding the trips to population-wide estimates. Based on the year of the survey, a variety of locations are coded. In earlier cycles, these include home, work or school, and other's home, whereas in later cycles these are augmented with locations such as grocery stores, restaurants, outdoor destinations, and others. The geographical resolution includes the province and whether the episode was in an urban or rural setting."

@@

{ActiveCA} is distributed as an `R` package with a number of data objects
and their documentation. `R` packages contain code, data, and
documentation in a standardized format that can be installed by R users
via a software repository, such as CRAN (Comprehensive R Archive
Network) or GitHub, which makes them an adroit medium to distribute
analysis-ready data.

@@

The Public Use Microdata are released by Statistics Canada in two files:
a *Main file* and an *Episode file*. The files are linked by keys that
identify households, individuals, and episodes (i.e., activities)
conducted by individuals. We discuss these files in more detail in the
following section.

## The Main file

The *Main file* of the time use survey compiles a large array of
aggregated data, summarizing the answers to the questionnaire that
describe households and individuals, as well as derived variables that
summarize the respondents' use of time use across different activities,
locations, and social interactions. This file documents the time and
duration that respondents allocate to each activity and location. The
*Main file* provides a overview of daily routines and social dynamics,
not focusing on individual activity episodes. Additionally, this file
categorizes activities into bigger groups and subcategories,
facilitating the data's analytical utility with additional metrics such
as total transit time, time spent with household members, and counts of
activities and episodes.

Table \ref{tab:main-2015-unprocessed} shows the first ten rows and first
six variables of the TUS PUMF 2015 *Main file* (Cycle 29). Each row in
the table correspond to a survey respondent, while the columns refer the
following information: record identification (`PUMFID`), the person's
weight (`WGHT_PER`), the month the survey data was collected (`SURVMNTH`),
the respondent's age group (`AGEGR10`), the respondent's sex (`SEX`), and
the respondent's marital status (`MARSTAT`).

The *Main file* of the 2015 GSS surveys includes a total of 17,390
respondents, representing `r sum(gss_m_2015$WGHT_PER)` individuals and
848 variables. For discrete variables, Statistics Canada has assigned
specific codes to the possible values, with each code accompanied by a
label. For instance, in the case of the variable `SURVMNTH`, a value of `1`
means `January 2016`, `2` means `February 2016`, `3` corresponds to `March 2016`,
and so on.

@@

```{r gss-main-file-2015}
main_2015_unprocessed <- gss_m_2015[1:10, 1:6]  |>
  kable(
    format = "latex", 
    booktabs = TRUE, 
    longtable = TRUE, 
    align = c(rep("c", ncol(gss_m_2015[1:10, 1:6]))),
    caption = "\\label{tab:main-2015-unprocessed}Visualization of the first ten lines and first six columns of the Main file of the 2015 GSS.") |>
  kable_styling(full_width = FALSE, 
                #latex_options=c("striped", "scale_down"), 
                latex_options=c("scale_down"),
                 font_size = 8) |>
  footnote(general = c("Legend: PUMFID: record identification. WGHT_PER:  person weight. SURVMNTH: survey month of data collection. AGEGR10: age group of the respondent. SEX: sex of the respondent. MARSTAT: marital status of the respondent."), threeparttable = T)

@@

## The Episode file

The episode is a much bigger file that records detailed data for each
activity episode reported by respondents. Each episode represents a
single activity and its duration, and the sum of all episodes throughout
the day adds up to 24 hours. Each entry in this file includes the start
and end times of the activity, the duration, location, and accompanying
social context, informing when and where activities occurred and with
whom. The focus of the *Episode file* is not on the characteristics of
the respondents, but on the characteristics of the activities, and the
data are structured around the numerous activity instances that compose
a day of the respondent. Although respondent-specific characteristics
are not included within the *Episode file*, it is possible to link the
*Main file* and the *Episode file* by using a key present in both the
*Main* and *Episode files*.

Similar to Table \ref{tab:main-2015-unprocessed}, which displayed an
example of the *Main file* structure, Table
\ref{tab:ep-2015-unprocessed} presents the first seven episodes for the
record identification number 10041 and some variables from the TUS PUMF
2015 *Episode file* (Cycle 29). Each row in the table corresponds to an
episode associated with the specified record identification (`PUMFID` =
`10041`), including the episode's weight (`WGHT_EPI`), episode number
(`EPINO`), activity code (`TUI_01`), episode duration (`DURATION`), and
episode location (`LOCATION`).

In total, the *Episode file* of the 2015 GSS surveys contains 274,108
records, representing `r sum(gss_e_2015$WGHT_EPI)` episodes and 527
variables detailing the episodes. Similar to the *Main file*, Statistics
Canada has created codes for the discrete variables, with each value
corresponding to a label.

In the case illustrated in Table \ref{tab:ep-2015-unprocessed}, this
respondent began the diary description by sleeping at home (`TUI_01 = 1`
and `LOCATION = 300`) for 210 minutes, followed by 40 minutes of personal
hygiene (`TUI_01 = 2`). The respondent then spent 15 minutes on personal
care activities, such as getting ready for school, supervising homework,
reading, playing, reprimanding, or providing educational or emotional
support, as indicated by `TUI_01 = 27.` Next, they recorded a travel
episode, walking for 15 minutes (`TUI_01 = 7` and `LOCATION = 315`), where
both the origin and destination were their home. Such trips, where the
journey starts and finishes at home, can be classified as recreational
or leisure trips. Next, the respondent spent 3 hours searching for a job
(`TUI_01 = 9`), took a 15-minute lunch break (`TUI_01 = 6`), and then
cleaned the house (`TUI_01 = 18`) for two hours. Table
\ref{tab:ep-2015-unprocessed} displays only six variables out of the 527
available. As shown, since the dataset does not label the variable
values, decoding them can be both time-consuming and challenging.

```{r gss-epi-file-2015}
ep_2015_unprocessed <- gss_e_2015 |>
  filter(PUMFID == 10041 & EPINO <= 7) |>
  dplyr::select(PUMFID, EPINO,WGHT_EPI,TUI_01, DURATION, LOCATION) |>
  kable(
    format = "latex", 
    booktabs = TRUE, 
    longtable = TRUE, 
    align = c(rep("c", ncol(gss_m_2015[1:10, 1:6]))),
    caption = "\\label{tab:ep-2015-unprocessed}Visualization of the seven first episodes of the record number 10041.") |>
  kable_styling(full_width = FALSE, 
                #latex_options=c("striped", "scale_down"), 
                latex_options=c("scale_down"),
                 font_size = 8) |>
  footnote(general = c("Legend: PUMFID: record identification. EPINO: episode number. WGHT_EPI: episode's weight. TUI_01: activity code. DURATION: episode's duration. LOCATION: episode's location."), threeparttable = T)

@@

Figure \ref{fig:process-figure} presents a diagram illustrating the
processes applied to the *Main* and *Episode files* to create the
{ActiveCA} datasets. For each TUS cycle, we reviewed the *Episode files*
to identify movement episodes involving walking or cycling. This allowed
us to also select the activities immediately before and after the
movement episode, helping to infer the trip’s purpose and determine its
origin and destination. Active trips were identified by their
corresponding activity codes, accounting for variations across survey
cycles.

@@

For the *Main files*, we selected socioeconomic variables to help
profile individuals engaged in active travel episodes. These included
key indicators such as age group, sex, marital status, and number of
children, among others. As with the *Episode files*, we labeled and
factored the coded variables. Using the appropriate identifiers, we
joined the Episode and *Main files* to determine the province and the
type of population centre - whether it is a CMA, a Census Agglomeration
(CA), or a non-CMA/CA area.

As output, the {ActiveCA} package provides processed datasets of walking
and cycling episodes by year, a unified dataset that contains all
walking and cycling episodes across TUS cycles, and processed main
files (not unified, as socioeconomic and demographic variables and
their categories differ across TUS cycles).

@@

Table \ref{tab:processed-obs} displays the total number of records
processed for Main and *Episode files*. For the *Main files*, a total of
`r sum(df_main_processed$Count)` records were processed, referring to
all records from the Time Use Surveys from 1986 to 2022, that together
represents more of `r sum(df_main_processed$Weighted)` respondents. It
also presents the total cases of active trips episodes identified. In
total `r sum(df_ep_processed$Count)` records with register of active
travel activity. Together, these records account for
`r sum(df_ep_processed$Weighted)` episodes.

@@

Table \ref{tab:main-2015-processed} shows the first ten rows and first
six variables of the TUS PUMF 2015 Main File (Cycle 29), displayed in
\ref{tab:main-2015-unprocessed} before our processing. Table
\ref{tab:ep-2015-processed} presents the walking episodes for the record
identification number `10041` from the TUS PUMF 2015 *Episode file* (Cycle
29), previously displayed in Table \ref{tab:ep-2015-unprocessed}. Only
the unique active travel episode appear in Table
\ref{tab:ep-2015-processed} since the records were filtered to select
cases with walking or cycling episodes. For both cases, Tables
\ref{tab:main-2015-processed} and \ref{tab:ep-2015-processed} contain
labeled variables, facilitating the interpretation of the data.

```{r gss-processed-file-2015, echo=FALSE, cache=FALSE}
main_2015_processed <- gss_main_2015[1:10, 1:6]  |>
  kable(
    format = "latex", 
    booktabs = TRUE, 
    longtable = TRUE, 
    align = c(rep("c", ncol(gss_m_2015[1:10, 1:6]))),
    caption = "\\label{tab:main-2015-processed}Visualization of the first ten lines and first six columns of the 2015 TUS Main File.") |>
  kable_styling(full_width = FALSE, 
                #latex_options=c("striped", "scale_down"), 
                latex_options=c("scale_down"),
                 font_size = 8) |>
  footnote(general = c("Legend: PUMFID: record identification. WGHT_PER:  person weight. SURVMNTH: survey month of data collection. AGEGR10: age group of the respondent. SEX: sex of the respondent. MARSTAT: marital status of the respondent."), threeparttable = T)

@@

ep_2015_unprocessed <- gss_episodes_renamed |>
  filter(PUMFID == 10041 & YEAR == 2015) |>
  dplyr::select(PUMFID, WGHT_EPI, act_label, DURATION, orig_label, dest_label, MODE) |>
  kable(
    format = "latex", 
    booktabs = TRUE, 
    longtable = TRUE, 
    caption = "\\label{tab:ep-2015-processed}Visualization of the active travel episode for the record number 10041 of the 2015 GSS survey.", 
       col.names = c("PUMFID", "WGHT_EPI","Activity","Duration","Origin", "Destination", "Mode")) |> 
  kable_styling(full_width = FALSE, 
                #latex_options=c("striped", "scale_down"), 
                latex_options=c("scale_down"),
                 font_size = 8) |>
  footnote(general = c("Legend: PUMFID: record identification. EPINO: episode number. WGHT_EPI: episode's weight. TUI_01: activity code. DURATION: episode's duration. LOCATION: episode's location."), threeparttable = T)

@@

# Latex table
median_duration_table <- median_duration_cma |>
  kable(
    format = "latex", 
    booktabs = TRUE, 
    caption = "\\label{tab:cma-durations}Differences in walking duration between provinces and population centre type.") |>
  kable_styling(full_width = FALSE, 
                #latex_options=c("striped", "scale_down"), 
                latex_options=c("scale_down"),
                 font_size = 8) |>
  add_header_above(c(" " = 1, "Population centre type" = 2)) |> 
  footnote(general = c("CMA denotes Census Metropolitan Area and CA denotes Census agglomeration."), threeparttable = T)

@@

{ActiveCA} also provides a Jupyter Notebook containing a `Python` script
that demonstrates how to read `R` data files (.rda) and convert them into
Pandas DataFrames. This process allows users to work with and utilize
the datasets available in {ActiveCA} within a `Python` project.

@@

The value of {ActiveCA} lies in its transparency, accessibility, and
ease of use, which facilitates the addition of complementary data sets
in the future. R users can seamlessly explore TUS walking and cycling
episodes, with the option to suggest enhancements to the package as
needed. This article adopts the structure proposed by Anastasia and Páez
[-@soukhov2023], whose work provided essential guidance for the creation
of this package. Similarly, we aim to contribute to the academic
community by promoting transparent research practices that encourage
replication and innovation in related fields. We believe that {ActiveCA}
will serve as a basis for further research on TUS and for the
integration of additional data by the authors or the wider open source
community.

@@

<https://user.fm/files/v2-3d261d0b2aa47fcad096cd9e49fd5cf8/ActiveCA.zip>
